The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-04-21 analysis/paper/paper.qmd
Add description of topic modeling as a specific type of clustering method

Similar to clustering on numeric data, topic modeling is a method of unsupervised classification of topics found in a group of documents [@silge2017].

>>>>

Similar to clustering on numeric data, topic modeling is a method of unsupervised classification of topics found in a group of documents [@silge2017]. An important distinction from other clustering methods like k-means, is that topic models allow for mixed membership. This means that a topic is a probability distribution over a vocabulary and that all words have a probability of being part of a topic. Typically, words with highest probablities within a topic will be examined to interpret and describe the meaning of a topic.
